### 2013-04-01 doc/final_report/methodology.tex
Added summary to methodology chapter

\section{ Initial Plan and Project Timeline }

@@

>>>>

\subsection{ Initial Plan and Project Timeline }

@@

\subsection{Support and Version Control Tools}

Partridge made heavy use of GitHub and the Git version control system. Git,
developed by Linus Torvalds, is a distributed Version Control System (VCS) that
offers many of the features of centralised VCSes such as Subversion and CVS.
However, unlike these centralised products, Git repositories are
self-contained, requiring no connection to a central server, with each copy of
the repository containing the complete project history. Copies of the
repositories are stored on the development machine, the production machine and
the GitHub server. This makes GIT more reliable than centralised repositories
since all code is accessible regardless of whether the repository hosted with
GitHub is online.

GitHub's hosted project management tools and wiki were used to store project
tasks, notes and metadata during development.

\section{Summary}

Having analysed some of the existing development methodologies and determined
that most of the common methodologies were not suitable for Partridge. A custom
methodology was formulated and support tools chosen. Task analysis was then
performed and a project timeline generated. With a timeline in place, the
initial design phase for Partridge and its subsystems could begin.
